A survey of HTTP caching implementations on the open Semantic Web

### 2015-03-12 sanity/paper1.tex
Explain the axes better
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1072 43ef1190-90fd-4dd7-a769-d0121f02b80e

In Figure~\ref{fig:hardall}, there is a barplot where
the freshness lifetime is grouped in bins. We see that in these
categories, the most common is to prohibit caching. Nevertheless, many
also declare a standards compliant freshness lifetime in minutes to
days\todo{explain number of occur}\todo{qqplot in report}.

\begin{figure}[ht]
  \centerline{%
    \includegraphics[width=.9\textwidth]{hardall.pdf}}
  \caption{Barplot counting all standards-compliant freshness lifetimes
    found, with the percentage of occurrences indicated on the
    bars. The first bin are the cases where caching is explicitly
    prohibited. The next bins are for lifetimes, where the values are
    grouped if they are on the order of seconds, minutes, hours, etc,
    i.e. the second bin counts the lifetimes in the interval [1,59]
    seconds, etc.}
  \label{fig:hardall}
\end{figure}

@@

\begin{figure}[th!]
  \centerline{%
    \includegraphics[width=.9\textwidth]{heuristicall.pdf}}
  \caption{Barplot counting all simple heuristic freshness lifetimes
    found. Bins as in Figure~\ref{fig:hardall}.}
  \label{fig:heuristicall}
\end{figure}

>>>>

In Figure~\ref{fig:hardall}, there is a barplot where
the freshness lifetime is grouped in bins. We see that in these
categories, the most common is to prohibit caching. Nevertheless, many
also declare a standards compliant freshness lifetime in minutes to
days\todo{qqplot in report}.

\begin{figure}[ht]
  \centerline{%
    \includegraphics[width=.9\textwidth]{hardall.pdf}}
  \caption{Barplot counting all standards-compliant freshness
    lifetimes found, with the percentage of occurrences indicated on
    the bars. On the horizontal axis, the first bin are the cases
    where caching is explicitly prohibited. The next bins are for
    lifetimes, where the values are grouped if they are on the order
    of seconds, minutes, hours, etc, i.e. the second bin counts the
    lifetimes in the interval [1,59] seconds, etc. On the vertical
    axis, the number of times a certain freshness lifetime was found.}
  \label{fig:hardall}
\end{figure}

@@

\begin{figure}[th!]
  \centerline{%
    \includegraphics[width=.9\textwidth]{heuristicall.pdf}}
  \caption{Barplot counting all simple heuristic freshness lifetimes
    found. Axes as in Figure~\ref{fig:hardall}.}
  \label{fig:heuristicall}
\end{figure}
